\documentclass[10pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\setlist[itemize]{leftmargin=*, itemsep=0.25mm, topsep=0.25mm}
\titlespacing*{\section}{0pt}{2mm}{1mm}
\setlength\parindent{0pt}
\linespread{0.95}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Daniel Smith}}\\[-1mm]
    \href{mailto:daniel@danielsmith.io}{daniel@danielsmith.io} \,|\, 
    \href{https://danielsmith.io}{danielsmith.io} \,|\, 
    \href{https://github.com/futuroptimist}{github.com/futuroptimist} \,|\, 
    \href{https://linkedin.com/in/danielsmith4483}{linkedin.com/in/danielsmith4483}
\end{center}

\vspace{-2mm}
\section*{Summary}
Site Reliability Engineer with 6+ years at YouTube (Google) delivering planet-scale reliability
through automation, observability, and on-call leadership. Builder of developer platforms and
AI-assisted tooling (flywheel, jobbot3000, sugarkube) that help teams ship safer software faster
across consumer, enterprise, and startup environments.

\vspace{-2mm}
\section*{Skills}
\textbf{Languages:} Python, Go, SQL, C++, JavaScript/TypeScript, Ruby, Objective\texttt{-}C \\
\textbf{Infra/Tools:} Borg (Google cluster manager), \textbf{Kubernetes}, \textbf{Docker}, GoogleSQL/BigQuery (\textbf{GCP}), GSLB, Linux, GitHub Actions, Three.js/WebGL, React/Next.js, Svelte, Astro \\
\textbf{Practices:} SRE (SLOs, incident response, capacity/reliability reviews), observability, CI/CD, testing, code health, \textbf{prompt docs \& agentic coding}, LLM prompt engineering

\vspace{-2mm}
\section*{Experience}
\textbf{YouTube (Google)} \hfill San Bruno, CA \\
\textit{Site Reliability Engineer (L4)} \hfill Sep 2018 -- May 2025
\begin{itemize}
  \item \textbf{Elevated reliability decisions:} Created reliability metrics and dashboards used by leadership to assess product health and prioritize fixes across surfaces.
  \item \textbf{Reduced toil and sped up detection:} Automated monitoring and analysis in Python, Go, SQL, and C++, improving signal quality for high-volume production systems.
  \item \textbf{Cross-org impact:} Consulted with teams across Alphabet to adopt consistent metrics and review methodologies; documented patterns and playbooks.
  \item \textbf{Incident operations:} On-call across Core SRE, Trust \& Safety SRE, and Search SRE; partnered with dev teams to improve runbooks and readiness.
  \item \textbf{LLM prototyping:} Built a Gemini-based summarizer for real-time in-app user feedback during a hackathon to surface actionable signals for triage.
  \item Promoted to \textbf{L4} in Dec 2021; mentored new engineers and strengthened onboarding.
\end{itemize}

\textbf{Naval Research Laboratory} \hfill Stennis Space Center, MS \\
\textit{Software Engineer} \hfill Jan 2017 -- Sep 2018
\begin{itemize}
  \item Delivered C++/Qt data-processing applications; shipped features in Scrum sprints with remote collaboration and shareable demos/docs.
\end{itemize}

\textbf{The University of Southern Mississippi} \hfill Hattiesburg, MS \\
\textit{Software Developer} \hfill Mar 2014 -- Dec 2016
\begin{itemize}
  \item Built an Objective-C content-delivery framework for university iOS apps; authored networking libraries for real-time content updates.
\end{itemize}

\vspace{-2mm}
\section*{Selected Open Source \& Personal Projects (GitHub: github.com/futuroptimist)}
\begin{itemize}
  \item \textbf{\href{https://democratized.space}{democratized.space}} - Retro-futurist text sim live
since 2022; offline-first quests teach real-world hobbies.
  \item \textbf{\href{https://token.place}{token.place}} - Peer-to-peer generative AI mesh where
encrypted compute tokens let volunteers share GPUs safely.
  \item \textbf{\href{https://github.com/futuroptimist/gabriel}{gabriel}} - Privacy-first guardian-angel
LLM delivering local security coaching and incident triage.
  \item \textbf{\href{https://github.com/futuroptimist/flywheel}{flywheel}} - GitHub template bundling
CI/tests/docs and \textbf{prompt docs}; cross-repo index in \texttt{docs/prompt-docs-summary.md}.
  \item \textbf{\href{https://github.com/futuroptimist/futuroptimist}{futuroptimist}} - Automated
YouTube video scripting pipeline stitching research, outlines, and narration-ready drafts.
  \item \textbf{\href{https://github.com/futuroptimist/f2clipboard}{f2clipboard}} - CLI that parses Codex
tasks and GitHub logs to ship concise debugging reports.
  \item \textbf{\href{https://github.com/futuroptimist/danielsmith.io}{danielsmith.io}} - Interactive
Three.js/WebGL portfolio (orthographic scene; keyboard navigation) with text-only fallback.
  \item \textbf{\href{https://github.com/futuroptimist/jobbot3000}{jobbot3000}} - Resume and interview-prep
pipeline (LLM-assisted prompts, templating, checklists).
  \item \textbf{\href{https://github.com/futuroptimist/sugarkube}{sugarkube}} - k3s plus Cloudflare-tunnel
hosting for personal sites; Raspberry Pi-friendly, outage-resistant.
\end{itemize}

\vspace{-2mm}
\section*{Education}
\textbf{The University of Southern Mississippi} - M.S. Computer Science, \textit{GPA: 4.0} \hfill Aug 2015 -- Aug 2016 \\
\textbf{The University of Southern Mississippi} - B.S. Computer Science, \textit{GPA: 4.0} \hfill May 2013 -- May 2015 \\
\textbf{Jones County Junior College} - A.A.S. Information System Technology, \textit{GPA: 4.0} \hfill Aug 2011 -- May 2013

\end{document}
